---
title: "QP: Data Analysis"
output:
  html_document:
    author: "Magali Lopez Cortez"
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
---

This notebook contains MDS and hierarchical clustering performed for selected themes (see QP_DataAnalysis for the criteria used to subset dataset) and *all roots* (as opposed to the analysis done in QP_DataAnalysis for a subset of 40 roots).

```{r "setup", include=FALSE}
#Load required packages
library(rdist)
library(tidyverse)
library(broom)
library(RColorBrewer)
library(superheat)
library(dendextend)
require("knitr")
```

# Dataset

Below are the first six rows of the dataset. Rows show Dispositional root + Speaker combination, and columns show themes/figures tested. Speakers were asked to provide a configuration for a given root+theme combination; if they provided it, the cells show a 1. If they said the combination was not possible, the cells show a 0. However, not all possible pairs of root+theme were tested, because of previous knowledge that that combination was not possible. Those cases are also coded with 0. Cases in which a participant was not asked an expected combination are coded NA. Marginal cases, that is, those in which participants were doubtful or showed that the root could be applied to only part of the figure tested, are coded 0.5. 

```{r}
#Import dataset
dataset <- read_csv("../QP_Data/disp_dataset.csv", col_types = cols(Root = col_factor(),
                                                                    Participant = col_factor()))
head(dataset)
```

```{r, include=FALSE}
# Calculate the proportion of speakers that found each root+theme pair acceptable
# This chunk of code can be improved to avoid repetition of the same code for each theme/figure - TO BE DONE

suum <- subset(dataset, select = c(Root,suum)) # create temporary dataset with one theme and list of roots
suum <- na.omit(suum) # delete rows with NA
count_suum <- suum %>% dplyr::count(Root) # count repetitions of roots (it will be 6 when there is no NA, less if there were NAs that got deleted)
suum <- aggregate(. ~ Root, suum, sum) # sum over column of theme for each root
suum <- mutate(suum,count=count_suum$n) # add count of roots to this dataset
suum <- mutate(suum,prop_suum=suum/count) # create column for proportion = sum of theme / count of root

tuunich <- subset(dataset, select = c(Root,tuunich))
tuunich <- na.omit(tuunich)
count_tuunich <- tuunich %>% dplyr::count(Root)
tuunich <- aggregate(. ~ Root, tuunich, sum)
tuunich <- mutate(tuunich,count=count_tuunich$n)
tuunich <- mutate(tuunich,prop_tuunich=tuunich/count)

nook <- subset(dataset, select = c(Root,nook))
nook <- na.omit(nook)
count_nook <- nook %>% dplyr::count(Root)
nook <- aggregate(. ~ Root, nook, sum)
nook <- mutate(nook,count=count_nook$n)
nook <- mutate(nook,prop_nook=nook/count)

che <- subset(dataset, select = c(Root,che))
che <- na.omit(che)
count_che <- che %>% dplyr::count(Root)
che <- aggregate(. ~ Root, che, sum)
che <- mutate(che,count=count_che$n)
che <- mutate(che,prop_che=che/count)

wiinik <- subset(dataset, select = c(Root,wiinik))
wiinik <- na.omit(wiinik)
count_wiinik <- wiinik %>% dplyr::count(Root)
wiinik <- aggregate(. ~ Root, wiinik, sum)
wiinik <- mutate(wiinik,count=count_wiinik$n)
wiinik <- mutate(wiinik,prop_wiinik=wiinik/count)

peek <- subset(dataset, select = c(Root,peek))
peek <- na.omit(peek)
count_peek <- peek %>% dplyr::count(Root)
peek <- aggregate(. ~ Root, peek, sum)
peek <- mutate(peek,count=count_peek$n)
peek <- mutate(peek,prop_peek=peek/count)

kaan <- subset(dataset, select = c(Root,kaan))
kaan <- na.omit(kaan)
count_kaan <- kaan %>% dplyr::count(Root)
kaan <- aggregate(. ~ Root, kaan, sum)
kaan <- mutate(kaan,count=count_kaan$n)
kaan <- mutate(kaan,prop_kaan=kaan/count)

taablaklaabos <- subset(dataset, select = c(Root,taablaklaabos))
taablaklaabos <- na.omit(taablaklaabos)
count_taablaklaabos <- taablaklaabos %>% dplyr::count(Root)
taablaklaabos <- aggregate(. ~ Root, taablaklaabos, sum)
taablaklaabos <- mutate(taablaklaabos,count=count_taablaklaabos$n)
taablaklaabos <- mutate(taablaklaabos,prop_taablaklaabos=taablaklaabos/count)

nalhek <- subset(dataset, select = c(Root,nalhek))
nalhek <- na.omit(nalhek)
count_nalhek <- nalhek %>% dplyr::count(Root)
nalhek <- aggregate(. ~ Root, nalhek, sum)
nalhek <- mutate(nalhek,count=count_nalhek$n)
nalhek <- mutate(nalhek,prop_nalhek=nalhek/count)

xim <- subset(dataset, select = c(Root,xim))
xim <- na.omit(xim)
count_xim <- xim %>% dplyr::count(Root)
xim <- aggregate(. ~ Root, xim, sum)
xim <- mutate(xim,count=count_xim$n)
xim <- mutate(xim,prop_xim=xim/count)

kamyoon <- subset(dataset, select = c(Root,kamyoon))
kamyoon <- na.omit(kamyoon)
count_kamyoon <- kamyoon %>% dplyr::count(Root)
kamyoon <- aggregate(. ~ Root, kamyoon, sum)
kamyoon <- mutate(kamyoon,count=count_kamyoon$n)
kamyoon <- mutate(kamyoon,prop_kamyoon=kamyoon/count)

ha <- subset(dataset, select = c(Root,ha))
ha <- na.omit(ha)
count_ha <- ha %>% dplyr::count(Root)
ha <- aggregate(. ~ Root, ha, sum)
ha <- mutate(ha,count=count_ha$n)
ha <- mutate(ha,prop_ha=ha/count)

plastilina <- subset(dataset, select = c(Root,plastilina))
plastilina <- na.omit(plastilina)
count_plastilina <- plastilina %>% dplyr::count(Root)
plastilina <- aggregate(. ~ Root, plastilina, sum)
plastilina <- mutate(plastilina,count=count_plastilina$n)
plastilina <- mutate(plastilina,prop_plastilina=plastilina/count)

luuch <- subset(dataset, select = c(Root,luuch))
luuch <- na.omit(luuch)
count_luuch <- luuch %>% dplyr::count(Root)
luuch <- aggregate(. ~ Root, luuch, sum)
luuch <- mutate(luuch,count=count_luuch$n)
luuch <- mutate(luuch,prop_luuch=luuch/count)

poomo <- subset(dataset, select = c(Root,poomo))
poomo <- na.omit(poomo)
count_poomo <- poomo %>% dplyr::count(Root)
poomo <- aggregate(. ~ Root, poomo, sum)
poomo <- mutate(poomo,count=count_poomo$n)
poomo <- mutate(poomo,prop_poomo=poomo/count)

maaskab <- subset(dataset, select = c(Root,maaskab))
maaskab <- na.omit(maaskab)
count_maaskab <- maaskab %>% dplyr::count(Root)
maaskab <- aggregate(. ~ Root, maaskab, sum)
maaskab <- mutate(maaskab,count=count_maaskab$n)
maaskab <- mutate(maaskab,prop_maaskab=maaskab/count)

hun <- subset(dataset, select = c(Root,hun))
hun <- na.omit(hun)
count_hun <- hun %>% dplyr::count(Root)
hun <- aggregate(. ~ Root, hun, sum)
hun <- mutate(hun,count=count_hun$n)
hun <- mutate(hun,prop_hun=hun/count)

arena <- subset(dataset, select = c(Root,arena))
arena <- na.omit(arena)
count_arena <- arena %>% dplyr::count(Root)
arena <- aggregate(. ~ Root, arena, sum)
arena <- mutate(arena,count=count_arena$n)
arena <- mutate(arena,prop_arena=arena/count)


# Join all columns with proportions into one dataset
df_prop <- data.frame(suum=suum$prop_suum, tuunich=tuunich$prop_tuunich, 
                      nook=nook$prop_nook, che=che$prop_che,
                      wiinik=wiinik$prop_wiinik, peek=peek$prop_peek,
                      kaan=kaan$prop_kaan, taablaklaabos=taablaklaabos$prop_taablaklaabos,
                      nalhek=nalhek$prop_nalhek, xim=xim$prop_xim,
                      kamyoon=kamyoon$prop_kamyoon, ha=ha$prop_ha,
                      plastilina=plastilina$prop_plastilina, luuch=luuch$prop_luuch,
                      poomo=poomo$prop_poomo, maaskab=maaskab$prop_maaskab,
                      hun=hun$prop_hun, arena=arena$prop_arena)
rootnames <- suum$Root

# Visualize first 6 rows of the new dataframe with the proportions of acceptability per root
head(df_prop)
```

# Multidimensional Scaling Analysis

```{r}
# Select figs/themes with less 0s
rootsTested <- 99 # (75% of 132) 
sub_allroots <- df_prop[,colSums(df_prop == 0) <= rootsTested]

# Select roots with less 0s
#sub <- mutate(sub_allroots, 'Root' = rootnames)
#rootnames <- sub$Root
#sub <- subset(sub, select = -c(Root)) 
#sub

# Calculate distance matrix using Euclidean distance
dm <- rdist(sub_allroots, metric="euclidean")

# Fit MDS
fit <- cmdscale(dm, eig=TRUE, x.ret=TRUE, k = 6)                       

# Calculate the percentage of variation that each MDS axis accounts for
var <- round(fit$eig/sum(fit$eig)*100, 1)

# Make a scree plot to show proportion of variance accounted for by each dimension
#jpeg("Figures/ScreePlotAllRoots.jpeg") #, res = 300, w = 2000, h = 1500
plot(fit$eig/sum(fit$eig), xlab="Dimensions", ylab="Proportion of variance")
#dev.off()

# Make a table to show proportion of variance accounted for by each dimension
var_table <- data.frame("Dimension"=c(1:6),"Variance"=var[1:6])
var_table

# Create data frame with solution
solution2 <- data.frame("Root" = rootnames,
                       "Dimension.1"=fit$points[,1],
                       "Dimension.2"=fit$points[,2],
                       "Dimension.3"=fit$points[,3],
                       "Dimension.4"=fit$points[,4],
                       "Dimension.5"=fit$points[,5],
                       "Dimension.6"=fit$points[,6])
```

# Hierarchical Clustering Analysis

```{r}
# Hierarchical clustering
library(usedist)
# Add labbels to dist matrix
dm <- dist_setNames(dm, rootnames)

# Create solution for clustering
clustering_solution <- hclust(dm, method="average")
plot(clustering_solution, cex=0.7)

```

```{r}
# Calculate silhouette widths (adapted from Levshina 2020)
library(cluster)
silwidths <- c()
for (i in 2:30){
silwidths <- c(silwidths, summary(silhouette(x = cutree(clustering_solution, k = i), dist = dm))$avg.width)
}
#jpeg("Figures/AvgSilWidths.jpeg")
plot(x = 2:30, silwidths, type = "b", xlab = "Number of clusters", ylab = "Average silhouette width")
#dev.off()
```

```{r}
colourCount = 21
getPalette = colorRampPalette(brewer.pal(12, "Paired"))

d <- as.dendrogram(clustering_solution,hang = 0.1)
#jpeg("Figures/ClustAllRoots.jpeg")
d %>% set("labels_col", getPalette(colourCount), k=21) %>% set("labels_cex", c(0.7)) %>% plot()
#dev.off()

#Get the labels based on the top 21 splits
ClusterLabel <- cutree(clustering_solution, k=21)
clust_labels_df <- data.frame(ClusterLabel) %>% rownames_to_column("Root")
#,row.names = rootnames
# Sort by Cluster label in increasing order
sort_clust_labels_df <- clust_labels_df[order(clust_labels_df$ClusterLabel), ]
sort_clust_labels_df
#write.csv(sort_clust_labels_df, file="Outputs/clustering_labels_AllRoots.csv", row.names=FALSE)
```

```{r}
# MDS plots
solution2 = mutate(solution2, 'ClusterLabel' = factor(clust_labels_df$ClusterLabel))
###############
# Dims 1 + 2
###############
#check_overlap = TRUE
#jpeg("Figures/MDSDims1-2AllRoots.jpeg")
plot1 <- ggplot(data=solution2, aes(x=Dimension.1, y=Dimension.2, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15), size=3, aes(colour = ClusterLabel)) + 
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 1 - ", var[1], "%", sep="")) +
  ylab(paste("Dim 2 - ", var[2], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5) 
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 2 + 1
###############
#jpeg("Figures/MDSDims2-1AllRoots.jpeg")
plot2 <- ggplot(data=solution2, aes(x=Dimension.2, y=Dimension.1, label=Root))+
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 2 - ", var[2], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 3 + 1
###############
#jpeg("Figures/MDSDims3-1AllRoots.jpeg")
plot3 <- ggplot(data=solution2, aes(x=Dimension.3, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 3 - ", var[3], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)   
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 4 + 1
###############
#jpeg("Figures/MDSDims4-1AllRoots.jpeg")
plot4 <- ggplot(data=solution2, aes(x=Dimension.4, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 4 - ", var[4], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 5 + 1
###############
#jpeg("Figures/MDSDims5-1AllRoots.jpeg")
plot5 <- ggplot(data=solution2, aes(x=Dimension.5, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 5 - ", var[5], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 6 + 1
###############
#jpeg("Figures/MDSDims6-1AllRoots.jpeg")
plot6 <- ggplot(data=solution2, aes(x=Dimension.6, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 6 - ", var[6], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()
#library(gridExtra)
#jpeg("Figures/MDSPlotsColor.jpeg", width = 1180, height = 1180,res=100)
#grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6)
#dev.off()
plot1
plot2
plot3
plot4
plot5
plot6
```
