---
title: "QP: Data Analysis"
output:
  html_document:
    author: "Magali Lopez Cortez"
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
---

This notebook contains MDS and hierarchical clustering performed for selected themes (see QP_DataAnalysis for the criteria used to subset dataset) and *all roots* (as opposed to the analysis done in QP_DataAnalysis for a subset of 40 roots).

```{r "setup", include=FALSE}
#Load required packages
library(rdist)
library(tidyverse)
library(broom)
library(RColorBrewer)
library(superheat)
library(dendextend)
require("knitr")
```

# Dataset

Below are the first six rows of the dataset. Rows show Dispositional root + Speaker combination, and columns show themes/figures tested. Speakers were asked to provide a configuration for a given root+theme combination; if they provided it, the cells show a 1. If they said the combination was not possible, the cells show a 0. However, not all possible pairs of root+theme were tested, because of previous knowledge that that combination was not possible. Those cases are also coded with 0. Cases in which a participant was not asked an expected combination are coded NA. Marginal cases, that is, those in which participants were doubtful or showed that the root could be applied to only part of the figure tested, are coded 0.5. 

```{r}
#Import dataset
dataset <- read_csv("../QP_Data/disp_dataset.csv", col_types = cols(Root = col_factor(),
                                                                    Participant = col_factor()))
head(dataset)
```

```{r, include=FALSE}
# Calculate the proportion of speakers that found each root+theme pair acceptable
# This chunk of code can be improved to avoid repetition of the same code for each theme/figure - TO BE DONE

suum <- subset(dataset, select = c(Root,suum)) # create temporary dataset with one theme and list of roots
suum <- na.omit(suum) # delete rows with NA
count_suum <- suum %>% dplyr::count(Root) # count repetitions of roots (it will be 6 when there is no NA, less if there were NAs that got deleted)
suum <- aggregate(. ~ Root, suum, sum) # sum over column of theme for each root
suum <- mutate(suum,count=count_suum$n) # add count of roots to this dataset
suum <- mutate(suum,prop_suum=suum/count) # create column for proportion = sum of theme / count of root

tuunich <- subset(dataset, select = c(Root,tuunich))
tuunich <- na.omit(tuunich)
count_tuunich <- tuunich %>% dplyr::count(Root)
tuunich <- aggregate(. ~ Root, tuunich, sum)
tuunich <- mutate(tuunich,count=count_tuunich$n)
tuunich <- mutate(tuunich,prop_tuunich=tuunich/count)

nook <- subset(dataset, select = c(Root,nook))
nook <- na.omit(nook)
count_nook <- nook %>% dplyr::count(Root)
nook <- aggregate(. ~ Root, nook, sum)
nook <- mutate(nook,count=count_nook$n)
nook <- mutate(nook,prop_nook=nook/count)

che <- subset(dataset, select = c(Root,che))
che <- na.omit(che)
count_che <- che %>% dplyr::count(Root)
che <- aggregate(. ~ Root, che, sum)
che <- mutate(che,count=count_che$n)
che <- mutate(che,prop_che=che/count)

wiinik <- subset(dataset, select = c(Root,wiinik))
wiinik <- na.omit(wiinik)
count_wiinik <- wiinik %>% dplyr::count(Root)
wiinik <- aggregate(. ~ Root, wiinik, sum)
wiinik <- mutate(wiinik,count=count_wiinik$n)
wiinik <- mutate(wiinik,prop_wiinik=wiinik/count)

peek <- subset(dataset, select = c(Root,peek))
peek <- na.omit(peek)
count_peek <- peek %>% dplyr::count(Root)
peek <- aggregate(. ~ Root, peek, sum)
peek <- mutate(peek,count=count_peek$n)
peek <- mutate(peek,prop_peek=peek/count)

kaan <- subset(dataset, select = c(Root,kaan))
kaan <- na.omit(kaan)
count_kaan <- kaan %>% dplyr::count(Root)
kaan <- aggregate(. ~ Root, kaan, sum)
kaan <- mutate(kaan,count=count_kaan$n)
kaan <- mutate(kaan,prop_kaan=kaan/count)

taablaklaabos <- subset(dataset, select = c(Root,taablaklaabos))
taablaklaabos <- na.omit(taablaklaabos)
count_taablaklaabos <- taablaklaabos %>% dplyr::count(Root)
taablaklaabos <- aggregate(. ~ Root, taablaklaabos, sum)
taablaklaabos <- mutate(taablaklaabos,count=count_taablaklaabos$n)
taablaklaabos <- mutate(taablaklaabos,prop_taablaklaabos=taablaklaabos/count)

nalhek <- subset(dataset, select = c(Root,nalhek))
nalhek <- na.omit(nalhek)
count_nalhek <- nalhek %>% dplyr::count(Root)
nalhek <- aggregate(. ~ Root, nalhek, sum)
nalhek <- mutate(nalhek,count=count_nalhek$n)
nalhek <- mutate(nalhek,prop_nalhek=nalhek/count)

xim <- subset(dataset, select = c(Root,xim))
xim <- na.omit(xim)
count_xim <- xim %>% dplyr::count(Root)
xim <- aggregate(. ~ Root, xim, sum)
xim <- mutate(xim,count=count_xim$n)
xim <- mutate(xim,prop_xim=xim/count)

kamyoon <- subset(dataset, select = c(Root,kamyoon))
kamyoon <- na.omit(kamyoon)
count_kamyoon <- kamyoon %>% dplyr::count(Root)
kamyoon <- aggregate(. ~ Root, kamyoon, sum)
kamyoon <- mutate(kamyoon,count=count_kamyoon$n)
kamyoon <- mutate(kamyoon,prop_kamyoon=kamyoon/count)

ha <- subset(dataset, select = c(Root,ha))
ha <- na.omit(ha)
count_ha <- ha %>% dplyr::count(Root)
ha <- aggregate(. ~ Root, ha, sum)
ha <- mutate(ha,count=count_ha$n)
ha <- mutate(ha,prop_ha=ha/count)

plastilina <- subset(dataset, select = c(Root,plastilina))
plastilina <- na.omit(plastilina)
count_plastilina <- plastilina %>% dplyr::count(Root)
plastilina <- aggregate(. ~ Root, plastilina, sum)
plastilina <- mutate(plastilina,count=count_plastilina$n)
plastilina <- mutate(plastilina,prop_plastilina=plastilina/count)

luuch <- subset(dataset, select = c(Root,luuch))
luuch <- na.omit(luuch)
count_luuch <- luuch %>% dplyr::count(Root)
luuch <- aggregate(. ~ Root, luuch, sum)
luuch <- mutate(luuch,count=count_luuch$n)
luuch <- mutate(luuch,prop_luuch=luuch/count)

poomo <- subset(dataset, select = c(Root,poomo))
poomo <- na.omit(poomo)
count_poomo <- poomo %>% dplyr::count(Root)
poomo <- aggregate(. ~ Root, poomo, sum)
poomo <- mutate(poomo,count=count_poomo$n)
poomo <- mutate(poomo,prop_poomo=poomo/count)

maaskab <- subset(dataset, select = c(Root,maaskab))
maaskab <- na.omit(maaskab)
count_maaskab <- maaskab %>% dplyr::count(Root)
maaskab <- aggregate(. ~ Root, maaskab, sum)
maaskab <- mutate(maaskab,count=count_maaskab$n)
maaskab <- mutate(maaskab,prop_maaskab=maaskab/count)

hun <- subset(dataset, select = c(Root,hun))
hun <- na.omit(hun)
count_hun <- hun %>% dplyr::count(Root)
hun <- aggregate(. ~ Root, hun, sum)
hun <- mutate(hun,count=count_hun$n)
hun <- mutate(hun,prop_hun=hun/count)

arena <- subset(dataset, select = c(Root,arena))
arena <- na.omit(arena)
count_arena <- arena %>% dplyr::count(Root)
arena <- aggregate(. ~ Root, arena, sum)
arena <- mutate(arena,count=count_arena$n)
arena <- mutate(arena,prop_arena=arena/count)


# Join all columns with proportions into one dataset
df_prop <- data.frame(suum=suum$prop_suum, tuunich=tuunich$prop_tuunich, 
                      nook=nook$prop_nook, che=che$prop_che,
                      wiinik=wiinik$prop_wiinik, peek=peek$prop_peek,
                      kaan=kaan$prop_kaan, taablaklaabos=taablaklaabos$prop_taablaklaabos,
                      nalhek=nalhek$prop_nalhek, xim=xim$prop_xim,
                      kamyoon=kamyoon$prop_kamyoon, ha=ha$prop_ha,
                      plastilina=plastilina$prop_plastilina, luuch=luuch$prop_luuch,
                      poomo=poomo$prop_poomo, maaskab=maaskab$prop_maaskab,
                      hun=hun$prop_hun, arena=arena$prop_arena)
rootnames <- suum$Root

# Visualize first 6 rows of the new dataframe with the proportions of acceptability per root
head(df_prop)
```

# Multidimensional Scaling Analysis

```{r}
# Select figs/themes with less 0s
rootsTested <- 99 # (75% of 132) 
sub_allroots <- df_prop[,colSums(df_prop == 0) <= rootsTested]

# Select roots with less 0s
#sub <- mutate(sub_allroots, 'Root' = rootnames)
#rootnames <- sub$Root
#sub <- subset(sub, select = -c(Root)) 
#sub

# Calculate distance matrix using Euclidean distance
dm <- rdist(sub_allroots, metric="euclidean")

# Fit MDS
fit <- cmdscale(dm, eig=TRUE, x.ret=TRUE, k = 6)                       

# Calculate the percentage of variation that each MDS axis accounts for
var <- round(fit$eig/sum(fit$eig)*100, 1)

# Make a scree plot to show proportion of variance accounted for by each dimension
#jpeg("Figures/ScreePlotAllRoots.jpeg") #, res = 300, w = 2000, h = 1500
plot(fit$eig/sum(fit$eig), xlab="Dimensions", ylab="Proportion of variance")
#dev.off()

# Make a table to show proportion of variance accounted for by each dimension
var_table <- data.frame("Dimension"=c(1:6),"Variance"=var[1:6])
var_table

# Create data frame with solution
solution2 <- data.frame("Root" = rootnames,
                       "Dimension.1"=fit$points[,1],
                       "Dimension.2"=fit$points[,2],
                       "Dimension.3"=fit$points[,3],
                       "Dimension.4"=fit$points[,4],
                       "Dimension.5"=fit$points[,5],
                       "Dimension.6"=fit$points[,6])
```

# Hierarchical Clustering Analysis

```{r}
# Hierarchical clustering
library(usedist)
# Add labbels to dist matrix
dm <- dist_setNames(dm, rootnames)

# Create solution for clustering
clustering_solution <- hclust(dm, method="average")
plot(clustering_solution, cex=0.7)

```

```{r}
# Calculate silhouette widths (adapted from Levshina 2020)
library(cluster)
silwidths <- c()
for (i in 2:30){
silwidths <- c(silwidths, summary(silhouette(x = cutree(clustering_solution, k = i), dist = dm))$avg.width)
}
#jpeg("Figures/AvgSilWidths.jpeg")
plot(x = 2:30, silwidths, type = "b", xlab = "Number of clusters", ylab = "Average silhouette width")
#dev.off()
```

```{r}
colourCount = 21
getPalette = colorRampPalette(brewer.pal(12, "Paired"))

d <- as.dendrogram(clustering_solution,hang = 0.1)
#jpeg("Figures/ClustAllRoots.jpeg")
d %>% set("labels_col", getPalette(colourCount), k=21) %>% set("labels_cex", c(0.7)) %>% plot()
#dev.off()

#Get the labels based on the top 21 splits
ClusterLabel <- cutree(clustering_solution, k=21)
clust_labels_df <- data.frame(ClusterLabel) %>% rownames_to_column("Root")
#,row.names = rootnames
# Sort by Cluster label in increasing order
sort_clust_labels_df <- clust_labels_df[order(clust_labels_df$ClusterLabel), ]
sort_clust_labels_df
#write.csv(sort_clust_labels_df, file="Outputs/clustering_labels_AllRoots.csv", row.names=FALSE)
```

```{r}
# MDS plots
solution2 = mutate(solution2, 'ClusterLabel' = factor(clust_labels_df$ClusterLabel))
###############
# Dims 1 + 2
###############
#check_overlap = TRUE
#jpeg("Figures/MDSDims1-2AllRoots.jpeg")
plot1 <- ggplot(data=solution2, aes(x=Dimension.1, y=Dimension.2, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15), size=3, aes(colour = ClusterLabel)) + 
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 1 - ", var[1], "%", sep="")) +
  ylab(paste("Dim 2 - ", var[2], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5) 
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 2 + 1
###############
#jpeg("Figures/MDSDims2-1AllRoots.jpeg")
plot2 <- ggplot(data=solution2, aes(x=Dimension.2, y=Dimension.1, label=Root))+
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 2 - ", var[2], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 3 + 1
###############
#jpeg("Figures/MDSDims3-1AllRoots.jpeg")
plot3 <- ggplot(data=solution2, aes(x=Dimension.3, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 3 - ", var[3], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)   
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 4 + 1
###############
#jpeg("Figures/MDSDims4-1AllRoots.jpeg")
plot4 <- ggplot(data=solution2, aes(x=Dimension.4, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 4 - ", var[4], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 5 + 1
###############
#jpeg("Figures/MDSDims5-1AllRoots.jpeg")
plot5 <- ggplot(data=solution2, aes(x=Dimension.5, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 5 - ", var[5], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()

###############
# Dims 6 + 1
###############
#jpeg("Figures/MDSDims6-1AllRoots.jpeg")
plot6 <- ggplot(data=solution2, aes(x=Dimension.6, y=Dimension.1, label=Root)) +
  geom_text(position=position_jitter(width=0.15,height=0.15),size=3, aes(colour = ClusterLabel)) +
  scale_fill_manual(values = getPalette(colourCount)) + #+ scale_color_brewer(palette="Paired") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlab(paste("Dim 6 - ", var[6], "%", sep="")) +
  ylab(paste("Dim 1 - ", var[1], "%", sep="")) + 
    xlim(-1.5, 1.5) +
    ylim(-1.5,1.5)  
  #ggtitle("MDS plot")
#dev.off()
#library(gridExtra)
#jpeg("Figures/MDSPlotsColor.jpeg", width = 1180, height = 1180,res=100)
#grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6)
#dev.off()
plot1
plot2
plot3
plot4
plot5
plot6
```
# Semantic categories

```{r,include=FALSE}
#Import dataset with semantic dimensions 
semdim <- read_csv("../QP_Data/Tilbe_dimensions.csv", col_types = cols(
  ROOT = col_factor(),
  Support = col_factor(),
  Leaning = col_factor(),
  Suspension = col_factor(),
  Blockage.of.motion = col_factor(),
  Orientation.in.vertical = col_factor(),
  Dispersion = col_factor(),
  Configuration.of.parts = col_factor(),
  Configuration.wrt.Ground= col_factor(),
  Containment = col_factor(),
  Length.of.vertical.dimension = col_factor(),
  Animate = col_factor(),
  Inanimate = col_factor(),
  Numerosity = col_factor(),
  Material.properties.specified = col_factor(),
  Potential.energy = col_factor(),
  Contact = col_factor()
  ))

# Change 0? and 1? into NAs
levels(semdim$Suspension)[levels(semdim$Suspension)=='1?'] <- NA
levels(semdim$Suspension)[levels(semdim$Suspension)==''] <- NA
levels(semdim$Support)[levels(semdim$Support)==''] <- NA
levels(semdim$Leaning)[levels(semdim$Leaning)==''] <- NA
levels(semdim$Configuration.of.parts)[levels(semdim$Configuration.of.parts)==''] <- NA
levels(semdim$Configuration.wrt.Ground)[levels(semdim$Configuration.wrt.Ground)==''] <- NA
levels(semdim$Containment)[levels(semdim$Containment)==''] <- NA
levels(semdim$Blockage.of.motion)[levels(semdim$Blockage.of.motion)=='0?'] <- NA
levels(semdim$Blockage.of.motion)[levels(semdim$Blockage.of.motion)==''] <- NA
levels(semdim$Orientation.in.vertical)[levels(semdim$Orientation.in.vertical)=='1?'] <- NA
levels(semdim$Orientation.in.vertical)[levels(semdim$Orientation.in.vertical)==''] <- NA
levels(semdim$Dispersion)[levels(semdim$Dispersion)=='1?'] <- NA
levels(semdim$Dispersion)[levels(semdim$Dispersion)==''] <- NA
levels(semdim$Length.of.vertical.dimension)[levels(semdim$Length.of.vertical.dimension)=='1?'] <- NA
levels(semdim$Length.of.vertical.dimension)[levels(semdim$Length.of.vertical.dimension)==''] <- NA
levels(semdim$Animate)[levels(semdim$Animate)=='1?'] <- NA
levels(semdim$Numerosity)[levels(semdim$Numerosity)=='1?'] <- NA
levels(semdim$Numerosity)[levels(semdim$Numerosity)=='0?'] <- NA
levels(semdim$Numerosity)[levels(semdim$Numerosity)==''] <- NA
levels(semdim$Material.properties.specified)[levels(semdim$Material.properties.specified)=='1?'] <- NA
levels(semdim$Material.properties.specified)[levels(semdim$Material.properties.specified)==''] <- NA
levels(semdim$Potential.energy)[levels(semdim$Potential.energy)=='1?'] <- NA
levels(semdim$Potential.energy)[levels(semdim$Potential.energy)==''] <- NA
levels(semdim$Contact)[levels(semdim$Contact)=='1?'] <- NA
levels(semdim$Contact)[levels(semdim$Contact)=='0?'] <- NA
levels(semdim$Contact)[levels(semdim$Contact)==''] <- NA

summary(semdim)
```

```{r,include=FALSE}
# Keep only those rows that have roots in common (between semantic dimensions and mds dimensions dataframes)
semdimdf <- semdim[which(semdim$ROOT %in% rootnames),]
mdsdimdf <- solution2[which(solution2$Root %in% semdimdf$ROOT),]

# Merge both dataframes into one
both <- cbind(semdimdf,mdsdimdf)
```

```{r,echo=FALSE}
# Boxplots Dim1 ~ .Semantic variables

# Prepare canvas
#jpeg("Figures/Dim1BoxplotsAllRoots.jpeg")
#par(mfrow=c(4,4))

# Check correlation between Dim1 and Animate
boxplot(both$Dimension.1 ~ both$Animate, ylab = "Dim 1", xlab = "Animate")

# Check correlation between Dim1 and Support
boxplot(both$Dimension.1 ~ both$Support,  ylab = "Dim 1", xlab = "Support")
#boxplot(both$Dimension.1 ~ both$Support, na.action=na.omit, ylab = "Dim 1", xlab = "Support")

# Check correlation between Dim1 and Leaning
boxplot(both$Dimension.1 ~ both$Leaning, ylab = "Dim 1", xlab = "Leaning")

# Check correlation between Dim1 and Suspension
boxplot(both$Dimension.1 ~ both$Suspension, ylab = "Dim 1", xlab = "Suspension")

# Check correlation between Dim1 and Blockage of motion
boxplot(both$Dimension.1 ~ both$Blockage.of.motion, ylab = "Dim 1", xlab = "Blockage of motion")

# Check correlation between Dim1 and Orientation in vertical
boxplot(both$Dimension.1 ~ both$Orientation.in.vertical, ylab = "Dim 1", xlab = "Orientation in vert")

# Check correlation between Dim1 and Dispersion
boxplot(both$Dimension.1 ~ both$Dispersion, ylab = "Dim 1", xlab = "Dispersion")

# Check correlation between Dim1 and Configuartion of parts
boxplot(both$Dimension.1 ~ both$Configuration.of.parts, ylab = "Dim 1", xlab = "Config. of parts")

# Check correlation between Dim1 and Configuration wrt Ground
boxplot(both$Dimension.1 ~ both$Configuration.wrt.Ground, ylab = "Dim 1", xlab = "Config. wrt ground")

# Check correlation between Dim1 and Containment
boxplot(both$Dimension.1 ~ both$Containment, ylab = "Dim 1", xlab = "Containment")

# Check correlation between Dim1 and Length of vertical dimension
boxplot(both$Dimension.1 ~ both$Length.of.vertical.dimension, ylab = "Dim 1", xlab = "Length of vert dim")

# Check correlation between Dim1 and Inanimate
boxplot(both$Dimension.1 ~ both$Inanimate, ylab = "Dim 1", xlab = "Inanimate")

# Check correlation between Dim1 and Numerosity
boxplot(both$Dimension.1 ~ both$Numerosity, ylab = "Dim 1", xlab = "Numerosity")

# Check correlation between Dim1 and Material properties specified
boxplot(both$Dimension.1 ~ both$Material.properties.specified, ylab = "Dim 1", xlab = "Material properties spec")

# Check correlation between Dim1 and Potential energy
boxplot(both$Dimension.1 ~ both$Potential.energy, ylab = "Dim 1", xlab = "Potential energy")

# Check correlation between Dim1 and Contact
boxplot(both$Dimension.1 ~ both$Contact, ylab = "Dim 1", xlab = "Contact")
#dev.off()
```
```{r,echo=FALSE}
# Boxplots Dim2 ~ .Semantic variables

# Prepare canvas
#jpeg("Dim2BoxplotsAllRoots.jpeg")
#par(mfrow=c(4,4))

# Check correlation between Dim2 and Animate
boxplot(both$Dimension.2 ~ both$Animate, ylab = "Dim 2", xlab = "Animate")

# Check correlation between Dim2 and Support
boxplot(both$Dimension.2 ~ both$Support, ylab = "Dim 2", xlab = "Support")

# Check correlation between Dim2 and Leaning
boxplot(both$Dimension.2 ~ both$Leaning, ylab = "Dim 2", xlab = "Leaning")

# Check correlation between Dim2 and Suspension
boxplot(both$Dimension.2 ~ both$Suspension, ylab = "Dim 2", xlab = "Suspension")

# Check correlation between Dim2 and Blockage of motion
boxplot(both$Dimension.2 ~ both$Blockage.of.motion, ylab = "Dim 2", xlab = "Blockage of motion")

# Check correlation between Dim2 and Orientation in vertical
boxplot(both$Dimension.2 ~ both$Orientation.in.vertical, ylab = "Dim 2", xlab = "Orientation in vert")

# Check correlation between Dim2 and Dispersion
boxplot(both$Dimension.2 ~ both$Dispersion, ylab = "Dim 2", xlab = "Dispersion")

# Check correlation between Dim2 and Configuartion of parts
boxplot(both$Dimension.2 ~ both$Configuration.of.parts, ylab = "Dim 2", xlab = "Config. of parts")

# Check correlation between Dim2 and Configuration wrt Ground
boxplot(both$Dimension.2 ~ both$Configuration.wrt.Ground, ylab = "Dim 2", xlab = "Config. wrt ground")

# Check correlation between Dim2 and Containment
boxplot(both$Dimension.2 ~ both$Containment, ylab = "Dim 2", xlab = "Containment")

# Check correlation between Dim2 and Length of vertical dimension
boxplot(both$Dimension.2 ~ both$Length.of.vertical.dimension, ylab = "Dim 2", xlab = "Length of vert dim")

# Check correlation between Dim2 and Inanimate
boxplot(both$Dimension.2 ~ both$Inanimate, ylab = "Dim 2", xlab = "Inanimate")

# Check correlation between Dim2 and Numerosity
boxplot(both$Dimension.2 ~ both$Numerosity, ylab = "Dim 2", xlab = "Numerosity")

# Check correlation between Dim2 and Material properties specified
boxplot(both$Dimension.2 ~ both$Material.properties.specified, ylab = "Dim 2", xlab = "Material properties spec")

# Check correlation between Dim2 and Potential energy
boxplot(both$Dimension.2 ~ both$Potential.energy, ylab = "Dim 2", xlab = "Potential energy")

# Check correlation between Dim2 and Contact
boxplot(both$Dimension.2 ~ both$Contact, ylab = "Dim 2", xlab = "Contact")
#dev.off()
```

```{r,echo=FALSE}
# Boxplots Dim3 ~ .Semantic variables

# Prepare canvas
#jpeg("Dim3BoxplotsAllRoots.jpeg")
#par(mfrow=c(4,4))

# Check correlation between Dim3 and Animate
boxplot(both$Dimension.3 ~ both$Animate, ylab = "Dim 3", xlab = "Animate")

# Check correlation between Dim3 and Support
boxplot(both$Dimension.3 ~ both$Support, ylab = "Dim 3", xlab = "Support")

# Check correlation between Dim3 and Leaning
boxplot(both$Dimension.3 ~ both$Leaning, ylab = "Dim 3", xlab = "Leaning")

# Check correlation between Dim3 and Suspension
boxplot(both$Dimension.3 ~ both$Suspension, ylab = "Dim 3", xlab = "Suspension")

# Check correlation between Dim3 and Blockage of motion
boxplot(both$Dimension.3 ~ both$Blockage.of.motion, ylab = "Dim 3", xlab = "Blockage of motion")

# Check correlation between Dim3 and Orientation in vertical
boxplot(both$Dimension.3 ~ both$Orientation.in.vertical, ylab = "Dim 3", xlab = "Orientation in vert")

# Check correlation between Dim3 and Dispersion
boxplot(both$Dimension.3 ~ both$Dispersion, ylab = "Dim 3", xlab = "Dispersion")

# Check correlation between Dim3 and Configuartion of parts
boxplot(both$Dimension.3 ~ both$Configuration.of.parts, ylab = "Dim 3", xlab = "Config. of parts")

# Check correlation between Dim3 and Configuration wrt Ground
boxplot(both$Dimension.3 ~ both$Configuration.wrt.Ground, ylab = "Dim 3", xlab = "Config. wrt ground")

# Check correlation between Dim3 and Containment
boxplot(both$Dimension.3 ~ both$Containment, ylab = "Dim 3", xlab = "Containment")

# Check correlation between Dim3 and Length of vertical dimension
boxplot(both$Dimension.3 ~ both$Length.of.vertical.dimension, ylab = "Dim 3", xlab = "Length of vert dim")

# Check correlation between Dim3 and Inanimate
boxplot(both$Dimension.3 ~ both$Inanimate, ylab = "Dim 3", xlab = "Inanimate")

# Check correlation between Dim3 and Numerosity
boxplot(both$Dimension.3 ~ both$Numerosity, ylab = "Dim 3", xlab = "Numerosity")

# Check correlation between Dim3 and Material properties specified
boxplot(both$Dimension.3 ~ both$Material.properties.specified, ylab = "Dim 3", xlab = "Material properties spec")

# Check correlation between Dim3 and Potential energy
boxplot(both$Dimension.3 ~ both$Potential.energy, ylab = "Dim 3", xlab = "Potential energy")

# Check correlation between Dim3 and Contact
boxplot(both$Dimension.3 ~ both$Contact, ylab = "Dim 3", xlab = "Contact")
#dev.off()
```