---
title: "QP: Data Analysis"
output:
  html_document:
    author: "Magali Lopez Cortez"
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
---

```{r "setup", include=FALSE}
#Set working directory, load required packages
#library(RColorBrewer)
library(rdist)
library(ggrepel)
library(ggiraph) 
library(anchors) # for replace.values
library(car)
library(tidyverse)
library(broom)
library(superheat)
require("knitr")
```

```{r}
#Import dataset
dataset <- read_csv("../QP_Data/disp_dataset.csv", col_types = cols(Root = col_factor(),
                                                                    Participant = col_factor()))
head(dataset)
```

```{r}
# Heatmap to visualize figs/themes with many 0s
figs <- subset(dataset, select = -c(Root,Participant))
superheat(figs, heat.na.col = "white", n.clusters.cols = 8, clustering.method = 'hierarchical', bottom.label = "variable", bottom.label.text.size = 2, bottom.label.text.angle = 90)
```

For each root+figure/theme pair, the idea is to find the proportion of speakers that found that pair acceptable. In this first trial, what I did was sum over each participant response for a given root+theme pair and divide that for the total number of participants. We might want to revisit this. Here's an example:

Root      | Participant     | ha
----      | -----           | ----- 
ak        | EMB             | 1 
ak        | FEE             | 1    
ak        | NMP             | NA
ak        | RMC             | 1
ak        | SBM             | 1
ak        | SME             | 1

This gives 5/6 = 0.83 acceptability for the ak+ha pair , so we're taking NAs as 0. 

In cases where speakers identified a root applicable to part of the figure (e.g. part of the body), I assigned that 0.5 (same with cases where speakers expressed doubt)

Root      | Participant     | kamyoon
----      | -----           | ----- 
boch'     | EMB             | 0.5 
boch'     | FEE             | 0.5    
boch'     | NMP             | 0
boch'     | RMC             | 0.5
boch'     | SBM             | 0
boch'     | SME             | 0.5

So 2/6 = 0.3 acceptability for the boch'+kamyoon pair.

```{r}
# Calculate proportions of participants that found a certain configuration acceptable for a particular pair root+figure
df <- aggregate(. ~ Root, dataset, sum)
# df <- select(df, -Participant) # for some reason this line of code started giving an error so changed it for the one below
rootnames <- df$Root
df <- subset(df, select = -c(Participant, Root))



# # Need to make this chunk of code more elegant:
# df_prop <- mutate(df, suum = suum/6, 
#                   tuunich = tuunich/6,
#                   nook = nook/6,
#                   che = che/6,
#                   wiinik = wiinik/6,
#                   peek = peek/6,
#                   kaan = kaan/6,
#                   taablaklaabos = taablaklaabos/6,
#                   nalhek = nalhek/6,
#                   xim = xim/6,
#                   kamyoon = kamyoon/6,
#                   ha = ha/6,
#                   plastilina = plastilina/6,
#                   luuch = luuch/6,
#                   poomo = poomo/6,
#                   maaskab = maaskab/6,
#                   hun = hun/6,
#                   arena = arena/6)

# Here
df_prop <- vector("double", ncol(df))  
for (i in seq_along(df)) {
  df_prop[[i]] <- df[i]/6
}
df_prop <- data.frame(df_prop)
df_prop
```



```{r}
# Calculate distance matrix using Euclidean distance
# dm <- rdist(subset(df_prop, select = -c(Root)), metric="euclidean")
dm <- rdist(subset(df_prop, metric="euclidean"))

# Fit MDS
fit <- cmdscale(dm, eig=TRUE, x.ret=TRUE, k = 3)                       

# fit returns:
# $points: a matrix with up to k columns whose rows give the coordinates of the points chosen to represent the dissimilarities
# $eig: the n eigenvalues computed during the scaling process if eig is true.
# $x: the doubly centered distance matrix if x.ret is true
# $ac: the additive constant c∗, 0 if add = FALSE 
## (When add = TRUE, a minimal additive constant c∗ is computed such that the dissimilarities dij+c∗ are Euclidean and hence can be represented in n - 1 dimensions)
# GOF: https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/cmdscale

# Calculate the percentage of variation that each MDS axis accounts for
var <- round(fit$eig/sum(fit$eig)*100, 1)

# Scree plot
plot(fit$eig/sum(fit$eig), xlab="Dimensions", ylab="Proportion of variance")

# Create data frame with solution
solution <- data.frame("Dimension.1"=fit$points[,1],
                       "Dimension.2"=fit$points[,2],
                       "Dimension.3"=fit$points[,3],
                       "Root" = rootnames)

```

```{r}
temp <- subset(dataset, select = -c(Participant, Root))
dims_themes <- cbind(solution,temp)
head(dims_themes)  
```

```{r}
# Plot one dimension
ggplot(data=solution, aes(x=Dimension.1, y=c(0), label=Root)) + geom_text() + geom_text_repel()
```

```{r}
# Boxplots Dim1 ~ .Themes

# Prepare canvas
par(mfrow=c(3,6))

# Check correlation between Dim1 and Animate
boxplot(dims_themes$Dimension.1 ~dims_themes$suum, ylab = "Dim 1", xlab = "Suum")
#summary(lm(Dimension.1 ~ Animate, data = both))

# Check correlation between Dim1 and Support
boxplot(dims_themes$Dimension.1 ~ dims_themes$tuunich, ylab = "Dim 1", xlab = "Tuunich")
#summary(lm(formula = Dimension.1 ~ Support, data = both))

# Check correlation between Dim1 and Leaning
boxplot(dims_themes$Dimension.1 ~ dims_themes$nook, ylab = "Dim 1", xlab = "Nook")
#summary(lm(formula = Dimension.1 ~ Leaning, data = both))

# Check correlation between Dim1 and Suspension
boxplot(dims_themes$Dimension.1 ~ dims_themes$che, ylab = "Dim 1", xlab = "Che")
#summary(lm(formula = Dimension.1 ~ Suspension, data = both))

# Check correlation between Dim1 and Blockage of motion
boxplot(dims_themes$Dimension.1 ~ dims_themes$wiinik, ylab = "Dim 1", xlab = "Wiinik")
#summary(lm(formula = Dimension.1 ~ Blockage.of.motion, data = both))

# Check correlation between Dim1 and Orientation in vertical
boxplot(dims_themes$Dimension.1 ~ dims_themes$peek, ylab = "Dim 1", xlab = "Peek")
#summary(lm(formula = Dimension.1 ~ Orientation.in.vertical, data = both))

# Check correlation between Dim1 and Dispersion
boxplot(dims_themes$Dimension.1 ~ dims_themes$kaan, ylab = "Dim 1", xlab = "Kaan")
#summary(lm(formula = Dimension.1 ~ Dispersion, data = both))

# Check correlation between Dim1 and Configuartion of parts
boxplot(dims_themes$Dimension.1 ~ dims_themes$taablaklaabos, ylab = "Dim 1", xlab = "Taabla/klaabos")
#summary(lm(formula = Dimension.1 ~ Configuration.of.parts, data = both))

# Check correlation between Dim1 and Configuration wrt Ground
boxplot(dims_themes$Dimension.1 ~ dims_themes$nalhek, ylab = "Dim 1", xlab = "Nal/hek")
#summary(lm(formula = Dimension.1 ~ Configuration.wrt.Ground, data = both))

# Check correlation between Dim1 and Containment
boxplot(dims_themes$Dimension.1 ~ dims_themes$xim, ylab = "Dim 1", xlab = "Xim")
#summary(lm(formula = Dimension.1 ~ Containment, data = both))

# Check correlation between Dim1 and Length of vertical dimension
boxplot(dims_themes$Dimension.1 ~ dims_themes$kamyoon, ylab = "Dim 1", xlab = "Kamyoon")
#summary(lm(formula = Dimension.1 ~ Length.of.vertical.dimension, data = both))

# Check correlation between Dim1 and Inanimate
boxplot(dims_themes$Dimension.1 ~ dims_themes$ha, ylab = "Dim 1", xlab = "Ha")
#summary(lm(formula = Dimension.1 ~ Inanimate, data = both))

# Check correlation between Dim1 and Numerosity
boxplot(dims_themes$Dimension.1 ~ dims_themes$plastilina, ylab = "Dim 1", xlab = "Plastilina")
#summary(lm(formula = Dimension.1 ~ Numerosity, data = both))

# Check correlation between Dim1 and Material properties specified
boxplot(dims_themes$Dimension.1 ~ dims_themes$luuch, ylab = "Dim 1", xlab = "Luuch")
#summary(lm(Dimension.1 ~ Material.properties.specified, data = both))

# Check correlation between Dim1 and Potential energy
boxplot(dims_themes$Dimension.1 ~ dims_themes$poomo, ylab = "Dim 1", xlab = "Poomo")
#summary(lm(formula = Dimension.1 ~ Potential.energy, data = both))

# Check correlation between Dim1 and Contact
boxplot(dims_themes$Dimension.1 ~ dims_themes$maaskab, ylab = "Dim 1", xlab = "Maaskab")
#summary(lm(formula = Dimension.1 ~ Contact, data = both))

boxplot(dims_themes$Dimension.1 ~ dims_themes$arena, ylab = "Dim 1", xlab = "Arena")
```


```{r}
# MDS plots

###############
# Dims 1 + 2
###############

# #Make a plot that shows the MDS axes 1 and 2 and the variation
# points <- fit$points
# plt <- data.frame(Root=dataset$Root,
#                             X=points[,1],
#                             Y=points[,2])
# plt <- mutate(plt, Root = df_prop$Root)
# 
# ggplot(data=plt, aes(x=X, y=Y, label=Root)) +
#   geom_text() +
#   #geom_text_repel() +
#   theme_bw() +
#   xlab(paste("Dim1 - ", var[1], "%", sep="")) +
#   ylab(paste("Dim2 - ", var[2], "%", sep="")) +
#   ggtitle("MDS plot")

ggplot(data=solution, aes(x=Dimension.1, y=Dimension.2, label=Root)) +
  geom_text() +
  #geom_text_repel() +
  theme_bw() +
  xlab(paste("Dim1 - ", var[1], "%", sep="")) +
  ylab(paste("Dim2 - ", var[2], "%", sep="")) +
  ggtitle("MDS plot")

###############
# Dims 2 + 3
###############

# Make a plot that shows the MDS axes 2 and 3 and the variation
# points <- fit$points
# plt <- data.frame(Root=rownames(points),
#                             X=points[,2],
#                             Y=points[,3])
# plt <- mutate(plt, Root = df_prop$Root)
# 
# 
# ggplot(data=plt, aes(x=X, y=Y, label=Root)) +
#   geom_text() +
#   theme_bw() +
#   xlab(paste("Dim2 - ", var[2], "%", sep="")) +
#   ylab(paste("Dim3 - ", var[3], "%", sep="")) +
#   ggtitle("MDS plot")

ggplot(data=solution, aes(x=Dimension.2, y=Dimension.3, label=Root)) +
  geom_text() +
  #geom_text_repel() +
  theme_bw() +
  xlab(paste("Dim2 - ", var[2], "%", sep="")) +
  ylab(paste("Dim3 - ", var[3], "%", sep="")) +
  ggtitle("MDS plot")

###############
# Dims 1 + 3
###############

# Make a plot that shows the MDS axes 1 and 3 and the variation
# points <- fit$points
# plt <- data.frame(Root=rownames(points),
#                             X=points[,1],
#                             Y=points[,3])
# plt <- mutate(plt, Root = df_prop$Root)
# 
# 
# ggplot(data=plt, aes(x=X, y=Y, label=Root)) +
#   geom_text() +
#   theme_bw() +
#   xlab(paste("Dim1 - ", var[1], "%", sep="")) +
#   ylab(paste("Dim3 - ", var[3], "%", sep="")) +
#   ggtitle("MDS plot")
ggplot(data=solution, aes(x=Dimension.1, y=Dimension.3, label=Root)) +
  geom_text() +
  #geom_text_repel() +
  theme_bw() +
  xlab(paste("Dim1 - ", var[1], "%", sep="")) +
  ylab(paste("Dim3 - ", var[3], "%", sep="")) +
  ggtitle("MDS plot")
```


```{r, echo=FALSE,include=FALSE}
# MDS plots with interactive labels

# Import and prepare glosses for interactive labels
roots_glosses <- read.delim("../QP_Data/roots_glosses.txt")
roots_glosses$Root <- as.factor(roots_glosses$Root)
roots_glosses$Gloss <- as.factor(roots_glosses$Gloss)
roots_glosses$rg <- paste(roots_glosses$Root, ":", roots_glosses$Gloss)

###############
# Dims 1 + 2
###############

# Make a plot that shows the MDS axes 1 and 2 and the variation
points <- fit$points
plt <- data.frame(Root=rownames(points),
                            X=points[,1],
                            Y=points[,2])
plt <- mutate(plt, Root = solution$Root)

onetwo <- ggplot(data=plt, aes(x=X, y=Y, label=Root)) +
  geom_text() +
  #geom_text_repel() +
  theme_bw() +
  xlab(paste("Dim1 - ", var[1], "%", sep="")) +
  ylab(paste("Dim2 - ", var[2], "%", sep="")) +
  ggtitle("MDS plot")

onetwogg <- onetwo + geom_point_interactive(aes(tooltip = roots_glosses$rg), size = 2)
ggiraph(code = print(onetwogg))
onetwogg

# To hover
#my_gg <- onetwogg + geom_point_interactive(
#    aes(tooltip = roots_glosses$rg, data_id = roots_glosses$rg), size = 2)
#ggiraph(code = print(my_gg))

###############
# Dims 2 + 3
###############

# Make a plot that shows the MDS axes 2 and 3 and the variation
points <- fit$points
plt <- data.frame(Root=rownames(points),
                            X=points[,2],
                            Y=points[,3])
plt <- mutate(plt, Root = solution$Root)


twothree <- ggplot(data=plt, aes(x=X, y=Y, label=Root)) +
  geom_text() +
  theme_bw() +
  xlab(paste("Dim2 - ", var[2], "%", sep="")) +
  ylab(paste("Dim3 - ", var[3], "%", sep="")) +
  ggtitle("MDS plot")

twothreegg <- twothree + geom_point_interactive(aes(tooltip = roots_glosses$rg), size = 2)
ggiraph(code = print(twothreegg))
twothreegg

###############
# Dims 1 + 3
###############

# Make a plot that shows the MDS axes 1 and 3 and the variation
points <- fit$points
plt <- data.frame(Root=rownames(points),
                            X=points[,1],
                            Y=points[,3])
plt <- mutate(plt, Root = solution$Root)


onethree <- ggplot(data=plt, aes(x=X, y=Y, label=Root)) +
  geom_text() +
  theme_bw() +
  xlab(paste("Dim1 - ", var[1], "%", sep="")) +
  ylab(paste("Dim3 - ", var[3], "%", sep="")) +
  ggtitle("MDS plot")

onethreegg <- onethree + geom_point_interactive(aes(tooltip = roots_glosses$rg), size = 2)
ggiraph(code = print(onethreegg))
onethreegg
```
 
 
```{r, include=FALSE}
# # Modify dataset for Hamming distance:
# # 0 = Not Acceptable
# # 1 = Acceptable
# # 2 = Acceptable for part of the figure / marginal acceptability
# # 3 = NA
# 
# # Replace 0.5 by 2
# dataset_ham <- replace.value(dataset, c("suum","tuunich","nook","che","wiinik","peek", "kaan", "taablaklaabos", "nalhek",
#                                         "xim", "kamyoon", "ha", "plastilina", "luuch", "poomo", "maaskab", "hun", "arena"), from=0.5, to=as.integer(2))
# 
# # Replace NA by 3
# dataset_ham <- replace.value(dataset_ham, c("suum","tuunich","nook","che","wiinik","peek", "kaan", "taablaklaabos", "nalhek",
#                                         "xim", "kamyoon", "ha", "plastilina", "luuch", "poomo", "maaskab", "hun", "arena"), from=NA, to=as.integer(3))
# 
# summary(dataset_ham)
# 
# # Have to merge roots!
```


```{r}
#Import dataset with semantic dimensions 
semdim <- read_csv("../QP_Data/Tilbe_dimensions.csv", col_types = cols(
  ROOT = col_factor(),
  Support = col_factor(),
  Leaning = col_factor(),
  Suspension = col_factor(),
  Blockage.of.motion = col_factor(),
  Orientation.in.vertical = col_factor(),
  Dispersion = col_factor(),
  Configuration.of.parts = col_factor(),
  Configuration.wrt.Ground= col_factor(),
  Containment = col_factor(),
  Length.of.vertical.dimension = col_factor(),
  Animate = col_factor(),
  Inanimate = col_factor(),
  Numerosity = col_factor(),
  Material.properties.specified = col_factor(),
  Potential.energy = col_factor(),
  Contact = col_factor()
  ))


# Change 0? and 1? into NAs
levels(semdim$Suspension)[levels(semdim$Suspension)=='1?'] <- NA
levels(semdim$Blockage.of.motion)[levels(semdim$Blockage.of.motion)=='0?'] <- NA
levels(semdim$Orientation.in.vertical)[levels(semdim$Orientation.in.vertical)=='1?'] <- NA
levels(semdim$Dispersion)[levels(semdim$Dispersion)=='1?'] <- NA
levels(semdim$Length.of.vertical.dimension)[levels(semdim$Length.of.vertical.dimension)=='1?'] <- NA
levels(semdim$Animate)[levels(semdim$Animate)=='1?'] <- NA
levels(semdim$Numerosity)[levels(semdim$Numerosity)=='1?'] <- NA
levels(semdim$Numerosity)[levels(semdim$Numerosity)=='0?'] <- NA
levels(semdim$Material.properties.specified)[levels(semdim$Material.properties.specified)=='1?'] <- NA
levels(semdim$Potential.energy)[levels(semdim$Potential.energy)=='1?'] <- NA
levels(semdim$Contact)[levels(semdim$Contact)=='1?'] <- NA
levels(semdim$Contact)[levels(semdim$Contact)=='0?'] <- NA

summary(semdim)


# Change 0? and 1? into 2s (for Hamming distance)
levels(semdimdf$Suspension)[levels(semdimdf$Suspension)=='1?'] <- 2
levels(semdimdf$Blockage.of.motion)[levels(semdimdf$Blockage.of.motion)=='0?'] <- 2
levels(semdimdf$Orientation.in.vertical)[levels(semdimdf$Orientation.in.vertical)=='1?'] <- 2
levels(semdimdf$Dispersion)[levels(semdimdf$Dispersion)=='1?'] <- 2
levels(semdimdf$Length.of.vertical.dimension)[levels(semdimdf$Length.of.vertical.dimension)=='1?'] <- 2
levels(semdimdf$Animate)[levels(semdimdf$Animate)=='1?'] <- 2
levels(semdimdf$Numerosity)[levels(semdimdf$Numerosity)=='1?'] <- 2
levels(semdimdf$Numerosity)[levels(semdimdf$Numerosity)=='0?'] <- 2
levels(semdimdf$Material.properties.specified)[levels(semdimdf$Material.properties.specified)=='1?'] <- 2
levels(semdimdf$Potential.energy)[levels(semdimdf$Potential.energy)=='1?'] <- 2
levels(semdimdf$Contact)[levels(semdimdf$Contact)=='1?'] <- 2
levels(semdimdf$Contact)[levels(semdimdf$Contact)=='0?'] <- 2

summary(semdimdf)
```
  
```{r}
# Keep only those rows that have roots in common (between semantic dimensions and mds dimensions dataframes)
semdimdf <- semdim[which(semdim$ROOT %in% rootnames),]
mdsdimdf <- solution[which(solution$Root %in% semdimdf$ROOT),]

# Merge both dataframes into one
both <- cbind(semdimdf,mdsdimdf)
```

```{r, include=FALSE}
#(dim1_anim)
# slope represents change from intercept (semdimdf$Animate = 0) towards semdimdf$Animate = 1

# # Change reference levels so that inanimate = 1 is ref
# both <- mutate(both, Inanimate  = factor (Inanimate), InRe = relevel(Inanimate, ref= '1'))
# # New boxplot and lm
# boxplot(formula = Dimension.1 ~ InRe, data = both)
# lm(formula = Dimension.1 ~ InRe, data = both)

# Try sum-coding
# both <- mutate(both, AnSum = Animate)
# contrasts(both$AnSum) <- contr.sum(2)
# lm (Dimension.1 ~ AnSum, data = both) %>% tidy %>% select(term, estimate)
# boxplot(Dimension.1 ~ AnSum, data = both)
# Use sum contrast coding for Tone
# triqui_3 <- mutate(triqui_2, Ctrd.Tone = factor(Tone))
# contrasts(both$Animate) <- contr.sum(2)
# contrasts(both$Animate)

# Multiple Regression Model
# summary(lm(formula = Dimension.1 ~ Animate + Support, data = both))
# summary(step <- step(lm(Dimension.1~1, data=both), Dimension.1~Animate+Support+Leaning+Suspension+Blockage.of.motion+Orientation.in.vertical+Dispersion+Configuration.of.parts+Configuration.wrt.Ground+Containment+Length.of.vertical.dimension+Inanimate+Numerosity+Material.properties.specified+Potential.energy+Contact))

##########
```

```{r}
# Boxplots Dim1 ~ .Semantic variables

# Prepare canvas
par(mfrow=c(3,6))

# Check correlation between Dim1 and Animate
boxplot(both$Dimension.1 ~ both$Animate, ylab = "Dim 1", xlab = "Animate")
#summary(lm(Dimension.1 ~ Animate, data = both))

# Check correlation between Dim1 and Support
boxplot(both$Dimension.1 ~ both$Support, ylab = "Dim 1", xlab = "Support")
#summary(lm(formula = Dimension.1 ~ Support, data = both))

# Check correlation between Dim1 and Leaning
boxplot(both$Dimension.1 ~ both$Leaning, ylab = "Dim 1", xlab = "Leaning")
#summary(lm(formula = Dimension.1 ~ Leaning, data = both))

# Check correlation between Dim1 and Suspension
boxplot(both$Dimension.1 ~ both$Suspension, ylab = "Dim 1", xlab = "Suspension")
#summary(lm(formula = Dimension.1 ~ Suspension, data = both))

# Check correlation between Dim1 and Blockage of motion
boxplot(both$Dimension.1 ~ both$Blockage.of.motion, ylab = "Dim 1", xlab = "Blockage of motion")
#summary(lm(formula = Dimension.1 ~ Blockage.of.motion, data = both))

# Check correlation between Dim1 and Orientation in vertical
boxplot(both$Dimension.1 ~ both$Orientation.in.vertical, ylab = "Dim 1", xlab = "Orientation in vert")
#summary(lm(formula = Dimension.1 ~ Orientation.in.vertical, data = both))

# Check correlation between Dim1 and Dispersion
boxplot(both$Dimension.1 ~ both$Dispersion, ylab = "Dim 1", xlab = "Dispersion")
#summary(lm(formula = Dimension.1 ~ Dispersion, data = both))

# Check correlation between Dim1 and Configuartion of parts
boxplot(both$Dimension.1 ~ both$Configuration.of.parts, ylab = "Dim 1", xlab = "Config. of parts")
#summary(lm(formula = Dimension.1 ~ Configuration.of.parts, data = both))

# Check correlation between Dim1 and Configuration wrt Ground
boxplot(both$Dimension.1 ~ both$Configuration.wrt.Ground, ylab = "Dim 1", xlab = "Config. wrt ground")
#summary(lm(formula = Dimension.1 ~ Configuration.wrt.Ground, data = both))

# Check correlation between Dim1 and Containment
boxplot(both$Dimension.1 ~ both$Containment, ylab = "Dim 1", xlab = "Containment")
#summary(lm(formula = Dimension.1 ~ Containment, data = both))

# Check correlation between Dim1 and Length of vertical dimension
boxplot(both$Dimension.1 ~ both$Length.of.vertical.dimension, ylab = "Dim 1", xlab = "Length of vert dim")
#summary(lm(formula = Dimension.1 ~ Length.of.vertical.dimension, data = both))

# Check correlation between Dim1 and Inanimate
boxplot(both$Dimension.1 ~ both$Inanimate, ylab = "Dim 1", xlab = "Inanimate")
#summary(lm(formula = Dimension.1 ~ Inanimate, data = both))

# Check correlation between Dim1 and Numerosity
boxplot(both$Dimension.1 ~ both$Numerosity, ylab = "Dim 1", xlab = "Numerosity")
#summary(lm(formula = Dimension.1 ~ Numerosity, data = both))

# Check correlation between Dim1 and Material properties specified
boxplot(both$Dimension.1 ~ both$Material.properties.specified, ylab = "Dim 1", xlab = "Material properties spec")
#summary(lm(Dimension.1 ~ Material.properties.specified, data = both))

# Check correlation between Dim1 and Potential energy
boxplot(both$Dimension.1 ~ both$Potential.energy, ylab = "Dim 1", xlab = "Potential energy")
#summary(lm(formula = Dimension.1 ~ Potential.energy, data = both))

# Check correlation between Dim1 and Contact
boxplot(both$Dimension.1 ~ both$Contact, ylab = "Dim 1", xlab = "Contact")
#summary(lm(formula = Dimension.1 ~ Contact, data = both))
```
```{r}
# T-test for correlation 
t.test(both$Dimension.1~both$Animate)
t.test(both$Dimension.1~both$Material.properties.specified)
```

```{r}
# Sum-coding for multiple categorical predictors
both <- mutate(both, AnSum = Animate)
contrasts(both$AnSum) <- contr.sum(2)
both <- mutate(both, MPSum = Material.properties.specified)
contrasts(both$MPSum) <- contr.sum(2)
both <- mutate(both, OVSum = Orientation.in.vertical)
contrasts(both$OVSum) <- contr.sum(2)

# Multiple Regression Model for Dim 1 testing Animate, Material.properties.specified 
# and Orientation in vertical as predictors
#summary(lm(Dimension.1 ~ Animate + Material.properties.specified, data = both))
dim1.AnMP <- lm(Dimension.1 ~ AnSum + MPSum, data = both)
summary(dim1.AnMP)

#summary(lm(Dimension.1 ~ Animate + Material.properties.specified + 
#             Orientation.in.vertical, data = both))
dim1.AnMPOV <- lm(Dimension.1 ~ AnSum + MPSum + 
             OVSum, data = both)
summary(dim1.AnMPOV)

#summary(lm(Dimension.1 ~ Animate + Orientation.in.vertical, data = both))
dim1.AnOV <- lm(Dimension.1 ~ AnSum + OVSum, data = both)
summary(dim1.AnOV)

# Assessing collinearity
vif(dim1.AnMP)
vif(dim1.AnMPOV)
vif(dim1.AnOV)
```

```{r}
# Boxplots Dim2 ~ .Semantic variables

# Prepare canvas
par(mfrow=c(3,6))

# Check correlation between Dim2 and Animate
boxplot(both$Dimension.2 ~ both$Animate, ylab = "Dim 2", xlab = "Animate")
#summary(lm(formula = Dimension.2 ~ Animate, data = both))

# Check correlation between Dim2 and Support
boxplot(both$Dimension.2 ~ both$Support, ylab = "Dim 2", xlab = "Support")
#summary(lm(formula = Dimension.2 ~ Support, data = both))

# Check correlation between Dim2 and Leaning
boxplot(both$Dimension.2 ~ both$Leaning, ylab = "Dim 2", xlab = "Leaning")
#summary(lm(formula = Dimension.2 ~ Leaning, data = both))

# Check correlation between Dim2 and Suspension
boxplot(both$Dimension.2 ~ both$Suspension, ylab = "Dim 2", xlab = "Suspension")
#summary(lm(Dimension.2 ~ Suspension, data = both))

# Check correlation between Dim2 and Blockage of motion
boxplot(both$Dimension.2 ~ both$Blockage.of.motion, ylab = "Dim 2", xlab = "Blockage of motion")
#summary(lm(formula = Dimension.2 ~ Blockage.of.motion, data = both))

# Check correlation between Dim2 and Orientation in vertical
boxplot(both$Dimension.2 ~ both$Orientation.in.vertical, ylab = "Dim 2", xlab = "Orientation in vert")
#summary(lm(formula = Dimension.2 ~ Orientation.in.vertical, data = both))

# Check correlation between Dim2 and Dispersion
boxplot(both$Dimension.2 ~ both$Dispersion, ylab = "Dim 2", xlab = "Dispersion")
#summary(lm(formula = Dimension.2 ~ Dispersion, data = both))

# Check correlation between Dim2 and Configuartion of parts
boxplot(both$Dimension.2 ~ both$Configuration.of.parts, ylab = "Dim 2", xlab = "Config. of parts")
#summary(lm(formula = Dimension.2 ~ Configuration.of.parts, data = both))

# Check correlation between Dim2 and Configuration wrt Ground
boxplot(both$Dimension.2 ~ both$Configuration.wrt.Ground, ylab = "Dim 2", xlab = "Config. wrt ground")
#summary(lm(formula = Dimension.2 ~ Configuration.wrt.Ground, data = both))

# Check correlation between Dim2 and Containment
boxplot(both$Dimension.2 ~ both$Containment, ylab = "Dim 2", xlab = "Containment")
#summary(lm(formula = Dimension.2 ~ Containment, data = both))

# Check correlation between Dim2 and Length of vertical dimension
boxplot(both$Dimension.2 ~ both$Length.of.vertical.dimension, ylab = "Dim 2", xlab = "Length of vert dim")
#summary(lm(formula = Dimension.2 ~ Length.of.vertical.dimension, data = both))

# Check correlation between Dim2 and Inanimate
boxplot(both$Dimension.2 ~ both$Inanimate, ylab = "Dim 2", xlab = "Inanimate")
#summary(lm(formula = Dimension.2 ~ Inanimate, data = both))

# Check correlation between Dim2 and Numerosity
boxplot(both$Dimension.2 ~ both$Numerosity, ylab = "Dim 2", xlab = "Numerosity")
#summary(lm(formula = Dimension.2 ~ Numerosity, data = both))

# Check correlation between Dim2 and Material properties specified
boxplot(both$Dimension.2 ~ both$Material.properties.specified, ylab = "Dim 2", xlab = "Material properties spec")
#summary(lm(formula = Dimension.2 ~ Material.properties.specified, data = both))

# Check correlation between Dim2 and Potential energy
boxplot(both$Dimension.2 ~ both$Potential.energy, ylab = "Dim 2", xlab = "Potential energy")
#summary(lm(formula = Dimension.2 ~ Potential.energy, data = both))

# Check correlation between Dim2 and Contact
boxplot(both$Dimension.2 ~ both$Contact, ylab = "Dim 2", xlab = "Contact")
#summary(lm(formula = Dimension.2 ~ Contact, data = both))
```
```{r}
# T-test for correlation 
t.test(both$Dimension.2~both$Suspension)
```

```{r}
# Sum-coding for multiple categorical predictors
both <- mutate(both, SuSum = Suspension)
contrasts(both$SuSum) <- contr.sum(2)
both <- mutate(both, PESum = Potential.energy)
contrasts(both$PESum) <- contr.sum(2)
both <- mutate(both, InSum = Inanimate)
contrasts(both$InSum) <- contr.sum(2)

# Multiple Regression Model for Dim 2 testing Suspension, Potential.energy
# and Inanimate as predictors
#summary(lm(formula = Dimension.2 ~ Suspension + Potential.energy, data = both))
dim2.SuPE <- lm(Dimension.2 ~ SuSum + PESum, data = both)
summary(dim2.SuPE)

#summary(lm(formula = Dimension.2 ~ Suspension + Potential.energy + 
#             Inanimate, data = both))
dim2.SuPEIn <- lm(Dimension.2 ~ SuSum + PESum + InSum, data = both)
summary(dim2.SuPEIn)

#summary(lm(formula = Dimension.2 ~ Suspension + Inanimate, data = both))
dim2.SuIn <- lm(Dimension.2 ~ SuSum + InSum, data = both)
summary(dim2.SuIn)
  
# Assessing collinearity
vif(dim2.SuPE)
vif(dim2.SuPEIn)
vif(dim2.SuIn)
```

```{r}
# Boxplots Dim3 ~ .Semantic variables

# Prepare canvas
par(mfrow=c(3,6))

# Check correlation between Dim3 and Animate
boxplot(both$Dimension.3 ~ both$Animate, ylab = "Dim 3", xlab = "Animate")
#summary(lm(formula = Dimension.3 ~ Animate, data = both))

# Check correlation between Dim3 and Support
boxplot(both$Dimension.3 ~ both$Support, ylab = "Dim 3", xlab = "Support")
#summary(lm(formula = Dimension.3 ~ Support, data = both))

# Check correlation between Dim3 and Leaning
boxplot(both$Dimension.3 ~ both$Leaning, ylab = "Dim 3", xlab = "Leaning")
#summary(lm(formula = Dimension.3 ~ Leaning, data = both))

# Check correlation between Dim3 and Suspension
boxplot(both$Dimension.3 ~ both$Suspension, ylab = "Dim 3", xlab = "Suspension")
#summary(lm(formula = Dimension.3 ~ Suspension, data = both))

# Check correlation between Dim3 and Blockage of motion
boxplot(both$Dimension.3 ~ both$Blockage.of.motion, ylab = "Dim 3", xlab = "Blockage of motion")
#summary(lm(formula = Dimension.3 ~ Blockage.of.motion, data = both))

# Check correlation between Dim3 and Orientation in vertical
boxplot(both$Dimension.1 ~ both$Orientation.in.vertical, ylab = "Dim 3", xlab = "Orientation in vert")
#summary(lm(formula = Dimension.1 ~ Orientation.in.vertical, data = both))

# Check correlation between Dim3 and Dispersion
boxplot(both$Dimension.3 ~ both$Dispersion, ylab = "Dim 3", xlab = "Dispersion")
#summary(lm(formula = Dimension.3 ~ Dispersion, data = both))

# Check correlation between Dim3 and Configuartion of parts
boxplot(both$Dimension.3 ~ both$Configuration.of.parts, ylab = "Dim 3", xlab = "Config. of parts")
#summary(lm(formula = Dimension.3 ~ Configuration.of.parts, data = both))

# Check correlation between Dim3 and Configuration wrt Ground
boxplot(both$Dimension.3 ~ both$Configuration.wrt.Ground, ylab = "Dim 3", xlab = "Config. wrt ground")
#summary(lm(formula = Dimension.3 ~ Configuration.wrt.Ground, data = both))

# Check correlation between Dim3 and Containment
boxplot(both$Dimension.3 ~ both$Containment, ylab = "Dim 3", xlab = "Containment")
#summary(lm(formula = Dimension.3 ~ Containment, data = both))

# Check correlation between Dim3 and Length of vertical dimension
boxplot(both$Dimension.3 ~ both$Length.of.vertical.dimension, ylab = "Dim 3", xlab = "Length of vert dim")
#summary(lm(formula = Dimension.3 ~ Length.of.vertical.dimension, data = both))

# Check correlation between Dim3 and Inanimate
boxplot(both$Dimension.3 ~ both$Inanimate, ylab = "Dim 3", xlab = "Inanimate")
#summary(lm(formula = Dimension.3 ~ Inanimate, data = both))

# Check correlation between Dim3 and Numerosity
boxplot(both$Dimension.3 ~ both$Numerosity, ylab = "Dim 3", xlab = "Numerosity")
#summary(lm(formula = Dimension.3 ~ Numerosity, data = both))

# Check correlation between Dim3 and Material properties specified
boxplot(both$Dimension.3 ~ both$Material.properties.specified, ylab = "Dim 3", xlab = "Material properties spec")
#summary(lm(formula = Dimension.3 ~ Material.properties.specified, data = both))

# Check correlation between Dim3 and Potential energy
boxplot(both$Dimension.3 ~ both$Potential.energy, ylab = "Dim 3", xlab = "Potential energy")
#summary(lm(formula = Dimension.3 ~ Potential.energy, data = both))

# Check correlation between Dim3 and Contact
boxplot(both$Dimension.3 ~ both$Contact, ylab = "Dim 3", xlab = "Contact")
#summary(lm(Dimension.3 ~ Contact, data = both))
```
```{r}
# T-test for correlation 
t.test(both$Dimension.3~both$Contact)
```

```{r}
# Sum-coding for multiple categorical predictors
both <- mutate(both, CoSum = Contact)
contrasts(both$CoSum) <- contr.sum(2)

# Multiple Regression Model for Dim 3 testing Contact, Orientation.in.veritcal,
# and Inanimate as predictors
#summary(lm(formula = Dimension.3 ~ Contact + Orientation.in.vertical, data = both))
dim3.CoOV <- lm(Dimension.3 ~ CoSum + OVSum, data = both)
summary(dim3.CoOV)
  
#summary(lm(formula = Dimension.3 ~ Contact + Orientation.in.vertical + 
#             Inanimate, data = both))
dm3.CoOVIn <- lm(Dimension.3 ~ CoSum + OVSum + InSum, data = both)
summary(dm3.CoOVIn)

#summary(lm(formula = Dimension.3 ~ Contact + Inanimate, data = both))
dim3.CoIn <- lm(Dimension.3 ~ CoSum + InSum, data = both)
summary(dim3.CoIn)
  
# Assessing collinearity
vif(dim3.CoOV)
vif(dm3.CoOVIn)
vif(dim3.CoIn)
```

```{r, include = FALSE}
# Divide roots according to support 1/0
supportyes <- both[both$Support == 1,]$ROOT
supportno <- both[both$Support == 0,]$ROOT
supportyes
supportno
```
